---
title: "Coronary Heart Disease Prediction"
author: "Mounika Yallamandhala"
date: "2023-04-28"
output: pdf_document
---

# Importing the data set

```{r setup}
train = read.csv("D:/MS/Michigan/Courses/Business analytics problem solving ITM 883/Project/train_data CV.csv")
test = read.csv("D:/MS/Michigan/Courses/Business analytics problem solving ITM 883/Project/test_data CV.csv")
train_quan_vars <- subset(train, select=c(sysBP, education, age, cigsPerDay, totChol, diaBP, BMI, heartRate, glucose))
round(cor(train_quan_vars, use="pairwise.complete.obs"), 2)
summary(train)
```


# Removing Missing values in the data

```{r}
missing_values = colSums(is.na(train))
print(missing_values)
train = na.omit(train)
sum(is.na(train))

missing_values_test = colSums(is.na(test))
print(missing_values_test)
test = na.omit(test)
sum(is.na(test))
```


# Target variable distribution

```{r}
freq = table(train$TenYearCHD)
perc = prop.table(freq)
my_colors <- c("green", "red")
my_labels <- c("0", "1")
pie(perc,labels = paste0(round(perc*100), "%"), col = my_colors, main = "TenYearCHD Binary Variable")
legend("topright", legend = my_labels, fill = my_colors)
```


# Removing id column from both train and test data set

```{r}
train = train[,-1]
test = test[,-1]
dim(train)
dim(test)
```


# Visualizing the data based on independent variables

```{r}
library(ggplot2)
ggplot(data=train) + geom_smooth(aes(x=BMI, y=TenYearCHD), method="glm",
                                 method.args = list(family = "binomial")) + 
  stat_summary(data=train, aes(x=round(BMI,-1), y=TenYearCHD), fun=mean, geom="point") +
  scale_y_continuous(labels = scales::percent_format()) + 
  theme_bw()

ggplot(data=train) + geom_smooth(aes(x=age, y=TenYearCHD), method="glm",
                                 method.args = list(family = "binomial")) + 
  stat_summary(data=train, aes(x=age, y=TenYearCHD), fun=mean, geom="point") +
  scale_y_continuous(labels = scales::percent_format()) + 
  theme_bw()
```


# Logistic Regression Model to predict dependent variable TenYearCHD using Age,Prevalent Stroke,  Prevalent Hyp, diaBP, BMI as independent variables

```{r}
model2 = glm(TenYearCHD ~ age + prevalentStroke + prevalentHyp + diaBP + BMI, data = train,
             family=binomial(link="logit"))
summary(model2)

library(pROC)
Predicted_prob = predict(model2, data=train, type="response")
ROC = roc(train$TenYearCHD,Predicted_prob)
plot(ROC)
```


# Finding best cut-off value

```{r}
coords(ROC,"best")
table(train$TenYearCHD)
ROC
```


# Confusion matrix

```{r}
threshold = 0.16
predicted_label <- ifelse(Predicted_prob > threshold , 1, 0)
actual_label <- train$TenYearCHD
confusion_matrix <- table(predicted_label, actual_label)
print(confusion_matrix)
```


# Calculate accuracy

```{r}
accuracy <- sum(diag(confusion_matrix)) / sum(confusion_matrix)
cat("Accuracy:", accuracy, "\n")
```


# Calculate precision and recall

```{r}
precision <- confusion_matrix[2,2] / sum(confusion_matrix[,2])
recall <- confusion_matrix[2,2] / sum(confusion_matrix[2,])
cat("Precision:", precision, "\n")
cat("Recall:", recall, "\n")
```

